One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2020-02-18 paper-v2.tex
up to "intensities for incomplete data"

A key concern with the two-stage approach is the propagation of the uncertainty from the detectability estimates to the second-stage spatial model.  Early attempts to address this focused on bootstrapping \citep{lahiri_resampling_2003, hedley_spatial_2004} but more recent work has pointed to potential difficulties of the bootstrapping approach, noting the difficulty of choosing the resampling units as well as the challenge of combining smoothers and spatial bootstraps \citep{bravington_reliable_2018-1}. Instead, \cite{bravington_reliable_2018-1}  proposed avoiding bootstrapping by propagating error based on a second-order Taylor approximation of detectability around the first-stage maximum-likelihood estimate.

Concerns about uncertainty propagation can be avoided by one-stage modelling approaches.  In our experience these tend to be developed within a Bayesian framework.  These approaches use data augmentation and to model unobserved individuals or groups and Markov-chain Monte Carlo (MCMC) methods for inference \citep{royle_hierarchical_2008, schmidt_using_2012}.  More recently  \cite{oedekoven_bayesian_2014} provided a one-stage model that avoids data augmention by specifying a combined likelihood of the detection and spatially-explicit count models and incorporated model uncertainty by applying a reversible jump MCMC algorithm.

The only Bayesian one-stage analysis that does not use MCMC is, to the best of our knowledge, \citet{yuan_point_2017} who use the approximate Bayesian method INLA applied to line transect data.  INLA can be an attractive choice when working with spatially-structured random effects in large or complex spatial domains.  The SPDE approach \citep{lindgren_explicit_2011} allows the construction of a sparse prior precision matrix which INLA can exploit for gains in computational efficiency and the finite element methods based on triangulation have been shown to be more efficient than regular lattice based approaches \citep{simpson_going_2016}, especially in applications with complex boundaries such as coastlines.

\citet{yuan_point_2017} also take a point process perspective and formulate the detection model as a thinning of the full but imperfectly observed point pattern.  Key to their approach was formulating the detection model using a stochastic partial differential equation.  Similar to spline approaches, choosing a B-spline basis and finite element methods results in a sparse prior precision matrix for the detection model coefficients which can then be incorporated into the latent-Gaussian model framework required by INLA.  Downsides to this approach are that it is challenging to mandate a monotonically decreasing detection function.  The authors suggestion to reject any non-monotonically decreasing functions when sampling from the posterior seems unsatisfactory.

Here we present a similar approach to \citet{yuan_point_2017} in that our models are fitted using INLA.  However, we avoid the SPDE detection model, instead allowing the user to specify a parametric family of detection functions, such as the half-normal.  This will be more familiar to users of traditional distance samplign approaches.  This results in components of the additive predictor that are non-linear in their parameters.  To deal with this we use a method of iterated model fits based on a Taylor expansion of the non-linear model components.  We name this approach \textit{iterated INLA}.

We also apply the methods to point transect data which require special treatment to account for the fact that the area surveyed increases with increasing distance from the observer.  Our case study is, to the best of our knowledge, the first analysis of point transect distance sampling data formulated as a thinned point process.  However, the point process viewpoint is not new and has been applied numerous times to line transect data \citep{buckland_model-based_2016, johnson_model-based_2010, hedley_spatial_2004,  hogmander_random_1991, stoyan_remark_1982}.  We also further develop the point process viewpoint to allow point process models to be applied to data with incomplete location information.  It is common for distance sampling surveys to only record the distance to the observer and the observer location.  We show how the point process perspective can still handle this type of data even though the exact location of the point cannot be drawn on a map.

@@

In this section we introduce the statistical model for the animal locations and observation process, including a detailed description of how this model can be represented as a modified Poisson likelihood.  We use this formulation to fit the model using the software package \texttt{inlabru} \citep{bachl_inlabru_2019}, an extension to the \texttt{R-INLA} implementation of INLA.

We assume the location of animals are a point pattern that follows a log-Gaussian Cox process with intensity process $\lambda(s)$.  The log-Gaussian Cox process is a flexible approach that can include spatially structured random effects on the intensity process to account for unexplained heterogeneity not captured by fixed-effect covariates.

\sloppy For the case with imperfect detection of points we specify a thinning probability function $g(s) = \mathbb{P}(\text{a point at $s$ is detected})$. A key property of the log-Gaussian Cox process is that a realisation of a point process with intensity process $\lambda(s)$ that is thinned by thinning probability function $g(s)$ also follows a log-Gaussian Cox process with intensity given by $\tl(s) = \lambda(s)g(s)$.

Standard distance sampling approaches specify $g(s)$ as a function that decays with increasing distance.  The distance measured depends on the type of survey.  For line transects the perpendicular distance to the transect line is used.  For point transects the horizontal distance to the observer is the relevant distance.  For the remainder of the paper we assume a point transect survey design.

The thinning probability function $g(s)$ is specified as a member of a parametric family of functions.  In this paper we demonstrate our approach using the half-normal formulation, although others such as hazard rate, are also common.  If $r(s)$ denotes the distance of a point at $s$ from the observer, the half-normal thinning probability function is $g(s | \sigma) = \exp(-r(s)^2 / 2\sigma^2)$ where $\sigma$ is a variance parameter to be estimated.  The parameter $\sigma$ can only be estimated if an assumption is made about the intensity of the animal locations.  Without such an assumption detectability and intensity are confounded.  The standard assumption in distance sampling is that the intensity is constant with respect to changes in $r(s)$.  Thus any observed differences from uniformity can be attributed to detectability and not variation in the intensity.

A point transect distance sampling survey consists of a set of $K$ sampling units.  The $k$-th sample unit we denote $\Omega_k \subset \mathbb{R}^2$ and the total surveyed region $\Omega = \cup_{k=1}^K \Omega_k$.  For simplicity we assume that all sampling units are discs with radius $W$ and $\Omega_j \cap \Omega_k = \emptyset$ for all $j \neq k$.  The thinning probability function $g(s)$ is defined relative to the positions of the sample units.  The probability of observing a point at location $s$ in the $k$-th sampling unit $\Omega_k$ we denote $g_k(s)$.  The probability of observing a point outside the surveyed region is zero.
Since the surveyed regions are non-overlapping each location $s \in \Omega$ is unambigiously associated with a single thinning probability function $g_k$.  For example, for an observer at location $s_k \in \Omega_k$, the half-normal thinning probability function is $g_k(s) = \exp(-\lVert s - s_k \rVert_2^2 / 2\sigma^2)$. The assumption of non-overlapping survey regions can be relaxed by including extra information such as the time of each observation but, for simplicity, we do not consider this here.  The thinning probability function for any $s \in \Omega$ is then given by $g(s) = g_{k(s)}(s)$ where $k(s) = k$ for $s \in \Omega_k$.

The thinned log-Gaussian Cox process likelihood with observed points at locations $\bm{Y} = (s_1, \ldots, s_n)^\intercal$ is then
\begin{equation}
\label{lgcp-likelihood}
\pi(\bm{Y}) = \exp\left(-\int\displaylimits_{s \in \Omega} \lambda(s) g(s) \mathrm{d}s \right)\prod_{i=1}^n \lambda(s_i)g(s_i)
\end{equation}
where we have suppressed parameter vector notation.  The integral component of the likelihood does not usually have analytical solutions.  Replacing the integral with a weighted sum allows the log-likelihood to be rewritten as a weighted Poisson log-likelihood, which we describe below, adapting the approach of \cite{simpson_going_2016} for a fully observed point pattern.

To evaluate the integral we introduce polar coordinates notation $s_k(r, \theta) = s_k + r\left[\cos\theta, \sin\theta \right]^T$ to represent locations in each sampling unit $\Omega_k$.   In general the thinning function depends only on $r$ and not on $\theta$.  We assume this is the case in the following and use the shorthand $g_k(r) = g(s_k(r, \theta))$. It follows that the integral can be rewritten as a sum of weighted one-dimensional integrals $\sum_{k=1}^K 2\pi \lambda(s_k) \int_0^W r g_k(r)\mathrm{d}r$ using the assumption that $\lambda(s)$ is constant within each sampling unit.  For each sampling unit we approximate the one-dimensional integral using a midpoint integration method with $M$ integration locations $r_{k1}, \ldots, r_{kM}$ and associated weights $\alpha_{k1}, \ldots, \alpha_{kM}$.  This gives
\begin{equation*}
	\int\displaylimits_{s \in \Omega} \lambda(s)g(s)\mathrm{d}s \approx \sum_{k=1}^K \sum_{j=1}^M \tilde{\alpha}_{kj} \tl(s_{kj})
\end{equation*}
where $\tilde{\alpha}_{kj} = 2\pi \alpha_{kj}r_{kj}$ and $\tl(s_{kj}) = \lambda(s_k) g_k(r_{kj})$.

To simplify notation below we let $\tilde{\alpha}_{k} = (\alpha_{k1}, \ldots, \alpha_{kM})^\intercal$ and $\tilde{\alpha} = (\alpha_1^\intercal, \ldots, \alpha_K^\intercal)^\intercal$.  Similarly let $\tl_k = (\tl(s_{k1}), \ldots, \tl(s_{kM}))^\intercal$, $\tl_{int} = (\tl_1^\intercal, \ldots, \tl_K^\intercal)^\intercal$ and denote the intensity evaluated at the observed locations as $\tl_{obs} = (\tl(s_1), \ldots, \tl(s_n))^\intercal$.  Then the approximate log-likelihood is
\begin{equation}
\label{approx-log-likelihood}
	\log \pi(\bm{Y}) \approx - \tilde{\alpha}^\intercal \tl_{int} + 1^\intercal\log\tl_{obs}
\end{equation}
This approximation can be written as a modified Poisson likelihood.  To see this let $\exp \eta = (\tl_{int}^\intercal, \tl_{obs}^\intercal)^\intercal$,
$\alpha = (\tilde{\alpha}^\intercal, 0_{n \times 1}^\intercal)^\intercal$ and construct a vector of pseudo-observations $y = (0_{KM\times 1}^\intercal, 1_{n \times 1}^\intercal)^\intercal$.  Then the approximate likelihood becomes
\begin{equation}
\pi(\bm{Y}) \approx \prod_{i=1}^{KM + n} \eta_i^{y_i}\exp(-\alpha_i\eta_i)
\end{equation}
This is similar to a Poisson likelihood with a $\log\alpha$ offset and can be specified using the Poisson likelihood implementation available in \texttt{R-INLA}.

@@

In the above we assume the data are complete records of animal location.  However, in many distance sampling surveys only the location of the observer and the distance to the observer are recorded.  Data of this type can be analysed within a point process framework by deriving the appropriate intensity function for the incomplete data.

Using the polar coordinates notation given above, for a detected point at location $s_k(r, \theta) \in \Omega_k$ we consider the case where we observe $r$ but not $\theta$.  It follows that the intensity for points at a distance $r$ observed within sampling unit $\Omega_k$ is
\begin{align}
\label{intensity-incomplete}
\tl_k(r) &= \oint\displaylimits_{c_k(r)} \lambda(s)g_k(s)\mathrm{d}s \nonumber \\
&= 2\pi\lambda(s_k)rg_k(r)
\end{align}
 where $c_k(r)$ is a circle of radius $r$ centred at $s_k$ and the second line follows from changing to polar coordinates and the assumption of constant intensity within $\Omega_k$.  This intensity differs from the full data case by including the $2\pi$  term to account for the fact that we do not observe $\theta$ and the additional $r$ term to account for the increasing area surveyed at larger distances.

@@

\section{Gaussian Markov random field spatial effect}

@@

Although we use a Bayesian approach, maximum-likelihood frameworks could also have been used for a one-stage analysis.  
Finally, we note that many of the themes addressed in this paper apply beyond the field of spatial ecology and will be of interest to the spatial statistics community in general, particularly for applications with complex observation models of latent processes and where spatial predictions are a key output of the analsyis.

@@

\clearpage
\bibliographystyle{chicago}
\bibliography{paper}

>>>>

A key concern with the two-stage approach is the propagation of uncertainty from the detectability estimates to the second-stage spatial model.  Early attempts to address this focused on bootstrapping \citep{lahiri_resampling_2003, hedley_spatial_2004} but more recent work has pointed to potential difficulties of the bootstrapping approach, noting the difficulty of choosing the resampling units when combining spatially structured random effects and spatial bootstraps \citep{bravington_reliable_2018-1}. Instead, \cite{bravington_reliable_2018-1} propose avoiding bootstrapping by propagating error based on a second-order Taylor approximation of detectability around the first-stage maximum-likelihood estimate.

Concerns about uncertainty propagation can be avoided by using one-stage modelling approaches.  These approaches tend to be Bayesian and use data augmentation and to model unobserved individuals or groups and Markov-chain Monte Carlo (MCMC) methods for inference (see )\citep{royle_hierarchical_2008, schmidt_using_2012}, for example).  \cite{oedekoven_bayesian_2014} demonstrate a one-stage model that avoids data augmentation by specifying a combined likelihood of the detection and spatially-explicit count models and incorporated model uncertainty using reversible jump MCMC.

The only Bayesian one-stage analysis that does not use MCMC is, to the best of our knowledge, \citet{yuan_point_2017}, who use the approximate Bayesian method of integrated nested Laplace approximations (INLA) \citep{rue_approximate_2009} applied to line transect distance sampling data.  INLA is a popular choice for fitting models with spatially-structured random effects in large or complex spatial domains due to the implementation of a computationally efficient approach based on the construction of a sparse prior precision matrix for the random effect parameters.  This sparse precision matrix specifies a GMRF representation of a Gaussian random field defined as the stationary solutions to an SPDE \citep{lindgren_explicit_2011} (see Section \ref{GMRFexplanation} for more details on this approach).  The finite element methods involved use a flexible triangulation of the spatial domain and have been shown to be more efficient than regular lattice based approaches \citep{simpson_going_2016}, a useful feature for applications with complex boundaries which appear in wildlife survey data such as boundaries formed by coastlines, rivers and other natural features.

\citet{yuan_point_2017} also take a point process perspective and formulate the detection model as a thinning of the full, but imperfectly observed, point pattern.  Key to their approach was formulating the detection model as the solution to an SPDE.  Choosing a B-spline basis and applying finite element methods results in a sparse prior precision matrix for the detection model coefficients which can then be incorporated into INLA using the same machinery as already exists for latent Gaussian precision matrices.  A major downside to this approach is that the solutions to the detection model SPDE are not necessarily monotonically decreasing - usually a key feature of detection functions.  The authors' suggestion to reject any non-monotonically decreasing functions when sampling from the posterior seems unsatisfactory.  It is also not clear how covariate effects on the detection function could be incorporated in this approach.

Here we present a related approach to the one in \citet{yuan_point_2017} in that our models are fitted using INLA.  However, we avoid these issues with the SPDE detection model, instead allowing the user to specify a parametric family of detection functions, such as the half-normal, as a user-written R function.  This approach of choosing a parametric family of detection functions will be more familiar to users of classical distance sampling methods than the SPDE specification.  However, this parametric form results in components of the additive predictor that are non-linear in their parameters, making model fitting infeasible in \text{R-INLA}.  We address this by using a method of iterated model fits based on a Taylor expansion of the non-linear model components.  We name this approach \textit{iterated INLA}.

We apply these methods to point transect \akepa data which differ from line transect methods to account for the fact that the area surveyed increases with increasing distance from the transect.  Our analysis is, to the best of our knowledge, the first analysis of point transect distance sampling data formulated as a thinned point process.  However, the point process viewpoint is not new and has been applied numerous times to line transect data \citep{buckland_model-based_2016, johnson_model-based_2010, hedley_spatial_2004,  hogmander_random_1991, stoyan_remark_1982, waagepetersen_likelihood-based_2006}.

@@

In this section we introduce the statistical model for the spatial pattern of animal locations and the observation process, including a detailed description of how this model can be written as a modified Poisson likelihood.  We use this formulation to fit the model using the software package \texttt{inlabru} \citep{bachl_inlabru_2019}, an extension to the \texttt{R-INLA} implementation of INLA, which implements the iterated INLA approach.

We assume the location of animals are a point pattern that follows a log-Gaussian Cox process with intensity process $\lambda(.)$, i.e.  the intensity at location $s$ is a random variable $\lambda(s)$.  The log-Gaussian Cox process is a flexible approach that can include spatial covariates to model the mean intensity and a mean-zero spatially structured random effect to account for unexplained heterogeneity not captured by the covariates \citep{moller_log_1998}.

To account for the imperfect detection of points we specify a thinning probability function $g(s) = \mathbb{P}(\text{a point at $s$ is detected})$. A key property of the log-Gaussian Cox process is that a realisation of a point process with intensity process $\lambda(s)$ that is thinned by thinning probability function $g(s)$ also follows a log-Gaussian Cox process with intensity given by $\tl(s) = \lambda(s)g(s)$.

Standard distance sampling approaches specify $g(s)$ as a function that decays with increasing distance.  The type of distance measured depends on the type of survey.  For line transects the perpendicular distance to the transect line is used.  For point transects the horizontal distance to the observer is the relevant distance.  For the remainder of the paper we assume a point transect survey design and hence horizontal distance to the observer located at the centre of the point transect.

The thinning probability function is specified as a parametric family of functions with parameter vector.  For example, if $r(s)$ denotes the distance of a point at $s$ from the observer, the half-normal thinning probability function is $g(s | \sigma) = \exp(-r(s)^2 / 2\sigma^2)$, where $\sigma$ is a variance parameter to be estimated.  Other types of detection function exist, such as hazard-rate, negative exponential, and they may or may not be adjusted using series expansions to add some flexibility to obtain a better fit to a given dataset \citep{buckland_distance_2015}.  In this analysis we assume a half-normal detection function with no covariates on detection parameters.

The detection function parameters can only be estimated if an assumption is made about the intensity of the animal locations.  Without such an assumption detectability and intensity are confounded.  The standard assumption in distance sampling is that the intensity is constant with respect to changes in $r(s)$.  Thus any observed deviations from uniformity can be attributed to detectability and not to variation in the intensity.

A point transect distance sampling survey consists of a set of $K$ point transects.   We denote $k$-th subset of space covered by the $k-th$ point transect as $\Omega_k \subset \mathbb{R}^2$ and the total surveyed region is $\Omega = \cup_{k=1}^K \Omega_k$.  For simplicity, we assume that all point transects are non-overlapping discs with radius $W$, as is the case in the HFBS survey.  The probability of observing a point at location $s \in \Omega_k$ we denote $g_k(s)$.  The probability of observing a point outside the surveyed region is zero.
Since the point transects are non-overlapping, each location $s \in \Omega$ is unambigiously associated with a single thinning probability function $g_k$.  For example, for an observer at location $s_k \in \Omega_k$, the half-normal thinning probability function is $g_k(s) = \exp(-\lVert s - s_k \rVert_2^2 / 2\sigma^2)$.  In practice the observer is always located at the centre of the point transect.  The assumption of non-overlapping survey regions could be relaxed by including extra information such as the time of each observation but this is not a requirement here.  The thinning probability function for any $s \in \Omega$ is then given by $g(s) = g_{k(s)}(s)$ where $k(s) = k$ for $s \in \Omega_k$.

The thinned log-Gaussian Cox process likelihood with observed points at locations $\bm{Y} = (s_1, \ldots, s_n)^\intercal$ is then
\begin{equation}
\label{lgcp-likelihood}
\pi(\bm{Y}) = \exp\left(-\int\displaylimits_{s \in \Omega} \lambda(s) g(s) \mathrm{d}s \right)\prod_{i=1}^n \lambda(s_i)g(s_i)
\end{equation}
where $\lambda(.)$ and $g(.)$ both depend on parameter vectors omitted for readability.

\subsection{Writing the model as a modified Poisson likelihood}

Here we show how to write the thinned log Gaussian Cox process model as a modified Poisson likelihood.  The integral component $\int\displaylimits_{s \in \Omega} \lambda(s) g(s) \mathrm{d}s$ in \autoref{lgcp-likelihood} does not have analytical solutions.  Replacing the integral with a weighted sum allows the log-likelihood to be rewritten as a weighted Poisson log-likelihood, which we describe below, adapting the approach developed by \cite{simpson_going_2016} for a fully observed point pattern.

To evaluate the integral we use polar coordinates notation $s_k(r, \theta) = s_k + r\left[\cos\theta, \sin\theta \right]^T$ to represent locations in each sampling unit $\Omega_k$.   In general, the thinning function depends only on $r$ and not on $\theta$.  We assume this is the case in the following and use the shorthand $g_k(r) = g(s_k(r, \theta))$. The integral can then be rewritten as a sum of weighted one-dimensional integrals $\sum_{k=1}^K 2\pi \lambda(s_k) \int_0^W r g_k(r)\mathrm{d}r$ using the assumption that $\lambda(s)$ is constant within each sampling unit.  For each sampling unit we approximate the one-dimensional integral using a midpoint integration method with $M$ integration locations $r_{k1}, \ldots, r_{kM}$ and associated weights $\alpha_{k1}, \ldots, \alpha_{kM}$.  This gives
\begin{equation*}
	\int\displaylimits_{s \in \Omega} \lambda(s)g(s)\mathrm{d}s \approx \sum_{k=1}^K \sum_{j=1}^M \tilde{\alpha}_{kj} \tl(s_{kj}) \;\;\; ,
\end{equation*}
where $\tilde{\alpha}_{kj} = 2\pi \alpha_{kj}r_{kj}$ and $\tl(s_{kj}) = \lambda(s_k) g_k(r_{kj})$.

To simplify notation below we let $\tilde{\alpha}_{k} = (\alpha_{k1}, \ldots, \alpha_{kM})^\intercal$ and $\tilde{\alpha} = (\alpha_1^\intercal, \ldots, \alpha_K^\intercal)^\intercal$.  Similarly, let $\tl_k = (\tl(s_{k1}), \ldots, \tl(s_{kM}))^\intercal$, $\tl_{int} = (\tl_1^\intercal, \ldots, \tl_K^\intercal)^\intercal$ and denote the intensity evaluated at the observed locations as $\tl_{obs} = (\tl(s_1), \ldots, \tl(s_n))^\intercal$.  Then the approximate log-likelihood is
\begin{equation}
\label{approx-log-likelihood}
	\log \pi(\bm{Y}) \approx - \tilde{\alpha}^\intercal \tl_{int} + 1^\intercal\log\tl_{obs}
\end{equation}
This approximation can be expressed as a modified Poisson likelihood.  To see this let $\exp \eta = (\tl_{int}^\intercal, \tl_{obs}^\intercal)^\intercal$,
$\alpha = (\tilde{\alpha}^\intercal, 0_{n \times 1}^\intercal)^\intercal$ and construct a vector of pseudo-observations $y = (0_{KM\times 1}^\intercal, 1_{n \times 1}^\intercal)^\intercal$.  Then the approximate likelihood becomes
\begin{equation}
\pi(\bm{Y}) \approx \prod_{i=1}^{KM + n} \eta_i^{y_i}\exp(-\alpha_i\eta_i)
\end{equation}
This is similar to a Poisson likelihood with offset $\log\alpha$ and can be specified using the Poisson likelihood implementated in \texttt{R-INLA} and \texttt{inlabru}.  The approach presented here is similar to the Berman-Turner device \citep{berman_approximating_1992, baddeley_practical_2000} although we relax the assumption that the observed points form part of the quadrature scheme.

@@

In the above, we assume the data are complete records of animal locations.  However, in many distance sampling surveys only the location of the observer and the distance to the observer are recorded.  Data of this type can be analysed within a point process framework by deriving the appropriate intensity function for the incomplete data as outlined below.

Using the polar coordinates notation given above, for a detected point at location $s_k(r, \theta) \in \Omega_k$ we consider the case where we observe $r$ but not $\theta$.  It follows that the intensity for points at a distance $r$ observed within sampling unit $\Omega_k$ is
\begin{align}
\label{intensity-incomplete}
\tl_k(r) &= \oint\displaylimits_{c_k(r)} \lambda(s)g_k(s)\mathrm{d}s \nonumber \\
&= 2\pi\lambda(s_k)rg_k(r) \;\;\; ,
\end{align}
 where $c_k(r)$ is a circle of radius $r$ centred at $s_k$ and the second line follows from changing to polar coordinates and the assumption of constant intensity within $\Omega_k$.  This intensity differs from the full data case by including the $2\pi$  term to account for the fact that we do not observe $\theta$ and the additional $r$ term to account for the increasing area surveyed at larger distances.

@@

\section{Gaussian Markov random field spatial effect}
\label{GMRFexplanation}

@@

Although we use a Bayesian approach, maximum-likelihood frameworks could also have been used for a one-stage analysis.  
Finally, we note that many of the themes addressed in this paper apply beyond the field of spatial ecology and will be of interest to the spatial statistics community in general, particularly for applications with complex observation models of latent processes and where spatial predictions are a key output of the analysis.

@@

\clearpage
\bibliographystyle{plainnat}
\bibliography{paper}
